\documentclass[oneside, 10pt]{memoir}

\usepackage{url}

\pagestyle{plain}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.25em}
\setlength{\partopsep}{0em}

\setheadfoot{0em}{1em}
\setlrmarginsandblock{2.5cm}{2.5cm}{*}
\setulmarginsandblock{2.5cm}{2.5cm}{*}
\checkandfixthelayout

\setaftersecskip{ 0em }

\begin{document}

% General Entry Command
% #1 : Flush Right (Heading)
% #2 : Flush Left (Heading)
% #3 : Body
\newcommand{\entryGeneral}[3]{
    \leftspringright{0.5}{0.5}{#2}{#1}%
    \begin{adjustwidth}{1em}{0em}%
        #3%
    \end{adjustwidth}
}

% ---------------------------------------------------------------------------------------------------------------------

% Title of CV
\LARGE{\textsc{Rollen D'Souza}}\\
\small{\url{rs2dsouz@edu.uwaterloo.ca}~\textbullet~\url{github.com/rollends} }\\
\rule{\textwidth}{0.4pt}

\section*{Publications}
\begin{adjustwidth}{1em}{0em}%
V. Joukov, R. D'Souza and D. Kuli\'{c}, \emph{Human pose estimation from imperfect sensor data via the Extended Kalman 
Filter}, International Symposium on Experimental Robotics, 2016. [Presented, In Print]
\end{adjustwidth}

\section*{Academic Work Experience}
\begin{adjustwidth}{1em}{0em}%
    \entryGeneral{2016/09\textemdash 2016/12}{\textbf{Teaching Assistant}}{
        Assisted students in the first year SE101 course. Managed a weekly 2-hour lab section and marked weekly quiz 
        submissions as well as a final course project. Engaged with students through Piazza and office hours.
    }
    
    \entryGeneral{2016/05\textemdash 2016/08}{\textbf{Undergraduate Research Assistant}}{
        Supervised by Prof. Dana Kuli\'{c}.
    }
    
    \entryGeneral{2015/01\textemdash 2015/04}{\textbf{Undergraduate Research Assistant}}{
        Implemented real-time inverse kinematics algorithm for human motion capture data. Supervised by Prof. 
        Dana Kuli\'{c}.
    }
\end{adjustwidth}

\section*{Industry Work Experience}
\begin{adjustwidth}{1em}{0em}%
    \entryGeneral{2015/09\textemdash 2015/12}{ 
        \textbf{Medical Software Developer Co-op} \\ 
        \emph{Sunnybrook Health Sciences Centre}} {
        C++ Linux and Windows Application development.
    }

    \entryGeneral{2014/05\textemdash 2014/08}{ 
        \textbf{Software Development Engineer Co-op} \\ 
        \emph{Coalition Game Studio, Microsoft}} {
        Created tools to support design and development workows in video games. Wrote rendering shaders and created 
        a background loader for the Unreal Game Engine. Contributed to \emph{Gears of War 3: Ultimate Edition} and 
        \emph{Gears of War 4}.
    }


\end{adjustwidth}

\end{document}
